---
title: "2023_09_CNM_Fall"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

#Libraries
```{r, Libraries}
library("rerddap")
library(tidyverse)
library("tidync")
library("doParallel")
library(lubridate)
library(patchwork)
library(viridis)
library(here)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(emmeans)
library(agricolae)
library(vegan)
library(performance)
library(broom)
library(car)
```

#Read in CSV
```{r, Read in CSV}
cnm_shell_length <- read_csv(here("Data","2023_09_CNM_OL_SL_Data.csv"))
cnm_mobiles <- read_csv(here("Data","2023_09_CNM_Mobile_Data.csv"))
cnm_mob_count_mat <- read_csv(here("Data", "2023_09_CNM_Mobile_Count_Matrix.csv"))
cnm_sessile_count_mat <- read_csv(here("Data", "2023_09_CNM_Sessile_Count_Matrix.csv"))
cnm_sessile <- read_csv(here("Data", "2023_09_CNM_Sessile_Data.csv"))
```

#Simple Statistics
```{r, Simple Statistics}
mean(cnm_shell_length$SL_mm)
max(cnm_shell_length$SL_mm)
min(cnm_shell_length$SL_mm)
```

#Density
```{r, Density}
cnm_area <- 140 # area (m^2) that I surveyed at Cabrillo National Monument Zone 3
cnm_total_limpets <- nrow(cnm_shell_length)
pop_density_cnm <- cnm_total_limpets/cnm_area #calculate population density # of limpet/m^2

```

#Population Shell Length Distribution Graph
```{r, Population Shell Length Distribution Graph}
cnm_pop_density <- cnm_shell_length %>% #calling csv with shell length data
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="purple",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Owl Limpet Population, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(cnm_shell_length$SL_mm),
             colour="green")#draw line where average lies on density
 cnm_pop_density
```

#Size Distribution of Tagged Limpets
```{r, Size Distribution of Tagged Limpets}
tagged_limpets <- cnm_shell_length %>% #named new data frame using shell length data
  filter(Tag_ID != 0) #filtered out non-tagged limpets
tagged_limpets #calling data frame
mean(tagged_limpets$SL_mm)
```

#Tagged Limpets Shell Length Distribution Graph
```{r, Tagged Limpets Shell Length Distribution Graph}
tagged_distribution <- tagged_limpets %>% #calling data frame with tagged limpets only
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="blue",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Tagged Owl Limpets, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 9),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_y_continuous(breaks = c(0,2,4,6,8,10))+ #lines I want to show up on y axis
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(tagged_limpets$SL_mm),
             colour="orange")#draw line where average lies on density
tagged_distribution
```

#Data Manipulation for Mobile Plots
```{r, Data Manipulation for Mobile Plots}
#Make some columns into factors
cnm_mobiles$COL_pres <- as.factor(cnm_mobiles$COL_pres) #made this coulmn a factor
cnm_mobiles$COL_pres_TF <- as.factor(cnm_mobiles$COL_pres_TF) #made this coulmn a factor THIS IMPORTANT FOR nMDS
cnm_mobiles$Transect<- as.factor(cnm_mobiles$Transect)


cnm_mobiles_long <- cnm_mobiles %>% 
  pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>%  #all counts of said species in this column, this can give me a count per species to get species abundance
  filter(Count != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected againts since they had 0 for all species
  group_by(COL_pres) %>% #group by presence or no presence of owl limpet
  count(Species) #provide count of each species by group
  #mutate(Spec_rich = (n/1963.5)*100) #create new column with species richness


cnm_mobiles_long_3 <- cnm_mobiles %>% 
  pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>%   #all counts of said species in this column, this can give me a count per species to get species abundance
  #filter(Count != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected againts since they had 0 for all species
  group_by(Plot_Name) %>% #group by presence or no presence of owl limpet
  count(Species) #provide count of each species by group

##########THIS IS THE ONE THAT WORKS############
cnm_mobiles_sum_spec <- cnm_mobiles %>% 
  mutate(spec_sum = rowSums(across(c(A_lugubris, L_plena, L_limatula, L_scabra, Nuttallina_sp, P_crassipes, T_funebralis, L_gigantea)), na.rm=TRUE)) %>% 
   pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count")
```

#Boxplot of Mobile Organism Abundance Per Plot in Presence/Absence of Central Limpet
```{r,Boxplot of Mobile Organism Abundance Per Plot in Presence/Absence of Central Limpet}
 cnm_mobiles_sum_spec %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Accent")+
  labs(title = "Abundance of Other Mobile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Abundance of Other Mobile Organisms") +
  theme_bw()
  
```


#Sessile Species Abundance Using Percent Cover
```{r, Sessile Species Abundance}
#Make columns into factors
cnm_sessile$COL_pres <- as.factor(cnm_sessile$COL_pres)
cnm_sessile$COL_pres_TF <- as.factor(cnm_sessile$COL_pres_TF) #made this coulmn a factor THIS IMPORTANT FOR nMDS
cnm_sessile$Transect<- as.factor(cnm_sessile$Transect)

cnm_sessile_sum_plot <- cnm_sessile %>% 
  mutate(spec_sum = rowSums(across(c(A_elegantissima,Chthalmus_sp, Bare_rock, Ralfsia_sp, P_polymerus, Ulva_sp)), na.rm=TRUE))%>% 
   pivot_longer(cols = A_elegantissima:Ulva_sp, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>% 
  mutate(count_sa = Count/spec_sum) %>% 
  mutate(percent_cover = count_sa*100)
```

#Boxplot of Sessile Organism Percent Cover Per Plot in Presence/Absence of Central Limpet
```{r, Boxplot of Sessile Organism Percent Cover Per Plot in Presence/Absence of Central Limpet}
cnm_sessile_sum_plot %>% 
  ggplot(aes(
    x = COL_pres,
    y = percent_cover,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Accent")+
  labs(title = "Percent Cover of Sessile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Percent Cover") +
  theme_bw()
```


#Permanova of mobile species abundance
```{r, Permanova of mobile species abundance}
cnm_mobiles_labels <- cnm_mobiles[,-c(1:7)] %>% #made labels using species names. It didn't work when I add this piece of code to the nMDS plot
  pivot_longer(cols = A_lugubris:L_gigantea,
               names_to = "Species",
               values_to = "Count")
                   
cnm_mobiles_sum <- cnm_mobiles%>% #I created a new data frame with the addition of the sum of individuals per species in each plot
  mutate(Sum = sum(A_lugubris, L_plena, L_limatula, L_scabra, Nuttallina_sp, P_crassipes, T_funebralis, L_gigantea)) %>% 
  filter(Sum != 0) #model doesn't work if sum column has 0s

cnm_mobiles_sum_pivot <- cnm_mobiles_sum %>% 
  pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>% 
  group_by(Plot_Name) %>% 
  count(Species)

model1<-adonis2(cnm_mobiles_sum[,-c(1:7)]~COL_pres_TF, cnm_mobiles_sum, permutations = 999, 
                method="bray")
model1
coeffs <- tidy(model1)
coeffs
```

#Permanova of Mobile Species Matrix
```{r, Permanova of Mobile Species Matrix}
cnm_mob_count_mat$COL_pres <- as.factor(cnm_mob_count_mat$COL_pres) #made this coulmn a factor
cnm_mob_count_mat$COL_pres_TF <- as.factor(cnm_mob_count_mat$COL_pres_TF) #made this coulmn a factor THIS IMPORTANT FOR nMDS
cnm_mob_count_mat$Transect<- as.factor(cnm_mob_count_mat$Transect)

cnm_mob_count_sum <- cnm_mob_count_mat%>% #I created a new data frame with the addition of the sum of counts per species in each plot using a data matrix made up of 0 and 1. 1 represents the occurence of that species in that plot.
  mutate(Sum = sum(A_lugubris, L_plena, L_limatula, L_scabra, Nuttallina_sp, P_crassipes, T_funebralis, L_gigantea)) %>% 
  filter(Sum != 0) #permanova did not accept 0

model2<-adonis2(cnm_mob_count_sum[,-c(1:7)]~COL_pres_TF, cnm_mob_count_sum, permutations = 999, method="bray") #independent variable is the presence or absence of limpets
model2
```

#nMDS of Mobile Species Abundance in the Presence/Absence of Owl Limpet
```{r, nMDS of Mobile Species in the Presence/Absence of Owl Limpet}
disper<-vegdist(cnm_mobiles_sum[,-c(1:7)]) #calculate distance matrix
cnm_mobile_distmat <- as.matrix(disper, labels = T) #used distance matrix as easy to view matrix


cnm_mobile_NMS <-
  metaMDS(cnm_mobile_distmat,#used metaMDS to make NMS to use in nMDS plot
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE)
cnm_mobile_NMS
cnm_mobile_NMS$stress
# Shepards test/goodness of fit
goodness(cnm_mobile_NMS) # Produces a results of test statistics for goodness of fit for each point

stressplot(cnm_mobile_NMS) # Produces a Shepards diagram

plot(cnm_mobile_NMS, #making nMDS plot, calling the NMS to use in formula
     ylim=c(-0.04,0.04)) %>% 
     points(points(cnm_mobile_NMS$points[cnm_mobiles_sum$COL_pres_TF=='TRUE',1],cnm_mobile_NMS$points[cnm_mobiles_sum$COL_pres_TF=='TRUE',2],
            pch=19, col='pink', cex=2)) %>% 
            points(points(cnm_mobile_NMS$points[cnm_mobiles_sum$COL_pres_TF=='FALSE',1],cnm_mobile_NMS$points[cnm_mobiles_sum$COL_pres_TF=='FALSE',2], 
                          pch=19, col='blue', cex=2)) %>% 
  ordiellipse(cnm_mobile_NMS, groups=cnm_mobiles_sum$COL_pres_TF, display = "sites", kind='ehull', border='black', col=c('blue','pink'), lwd=2, draw ='polygon')
```


#nMDS of Mobile Species Richness in the Presence/Absence of Owl Limpet
```{r, nMDS of Mobile Species Richness in the Presence/Absence of Owl Limpet}
disper<-vegdist(cnm_mob_count_sum[,-c(1:7)])#calculate distance matrix
cnm_mob_count_sum_distmat <- as.matrix(disper, labels = T) #easy to view matrix


cnm_mob_count_NMS <-metaMDS(cnm_mob_count_sum_distmat, #used metaMDS to make NMS to use in nMDS plot
          distance = "bray",
          k = 2,
          maxit = 999, 
          trymax = 500,
          wascores = TRUE)
# Shepards test/goodness of fit
goodness(cnm_mob_count_NMS) # Produces a results of test statistics for goodness of fit for each point

stressplot(cnm_mob_count_NMS) # Produces a Shepards diagram

plot(cnm_mob_count_NMS,
     ylim=c(-0.02,0.02)) %>% 
     points(points(cnm_mob_count_NMS$points[cnm_mob_count_sum$COL_pres_TF=='TRUE',1],cnm_mob_count_NMS$points[cnm_mob_count_sum$COL_pres_TF=='TRUE',2],
            pch=19, col='purple', cex=2)) %>% 
            points(points(cnm_mob_count_NMS$points[cnm_mob_count_sum$COL_pres_TF=='FALSE',1],cnm_mob_count_NMS$points[cnm_mob_count_sum$COL_pres_TF=='FALSE',2], 
                          pch=19, col='green', cex=2)) %>% 
  ordiellipse(cnm_mob_count_NMS, groups=cnm_mob_count_sum$COL_pres_TF, display = "sites", kind='ehull', border='black', col=c('green','purple'), lwd=2, draw ='polygon')
```

#Linear Regression of Limpet Presence/absence vs total mobile abundance per Transect
```{r, Linear Regression of Limpet Presence/absence vs total mobile abundance}
cnm_mobiles_long_2 <- cnm_mobiles %>% 
  pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>%  #all counts of said species in this column, this can give me a count per species to get species richness
  filter(Count != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected against since they had 0 for all species
  group_by(Transect, COL_pres) %>% 
  count(Species)# %>% #provide count of each species by group
  #mutate(Spec_rich = (n/1963.5)*100)
model_mob_lin_reg <- glm(COL_pres~n, family = "binomial"(link = "logit"), data = cnm_mobiles_long_2)
model_mob_lin_reg
Anova(model_mob_lin_reg)

library(pscl)
pR2(model_mob_lin_reg)


#########MIGHT GO WITH THIS ONE###############
model2_mob_lin_reg <- glm(COL_pres~spec_sum, family = "binomial"(link = "logit"), data = cnm_mobiles_sum_spec)
model2_mob_lin_reg
Anova(model2_mob_lin_reg)
pR2(model2_mob_lin_reg)
```

#Linear Regression of Sessile Percent Cover vs Presence/absence of Owl limpet
```{r, Linear Regression of Sessile Percent Cover vs Presence/absence of Owl limpet}
model1_sessile_lin_reg <- glm(COL_pres~Count, family = "binomial"(link = "logit"), data = cnm_sessile_sum_plot)
model1_sessile_lin_reg
Anova(model1_sessile_lin_reg)
pR2(model1_sessile_lin_reg)
```


#Species Richness of Mobiles
```{r, Species Richness of Mobiles}
cnm_mob_count_mat$COL_pres <- as.factor(cnm_mob_count_mat$COL_pres) #made this coulmn a factor
cnm_mob_count_mat$COL_pres_TF <- as.factor(cnm_mob_count_mat$COL_pres_TF) #made this coulmn a factor THIS IMPORTANT FOR nMDS
cnm_mob_count_mat$Transect<- as.factor(cnm_mob_count_mat$Transect)

cnm_mob_count_mat_long <- cnm_mob_count_mat %>% 
  pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Values") %>%  #all counts of said species in this column, this can give me a count per species to get species richness
  filter(Values != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected againts since they had 0 for all species
  group_by(COL_pres) %>% #group by presence or no presence of owl limpet
  count(Species)

cnm_mob_count_mat_sum <- cnm_mob_count_mat %>% 
  mutate(spec_sum = rowSums(across(c(A_lugubris, L_plena, L_limatula, L_scabra, Nuttallina_sp, P_crassipes, T_funebralis, L_gigantea)), na.rm=TRUE))
```


#Species Richness of Mobiles Boxplot
```{r, Species Richness of Mobiles Boxplot}
mobile_spec_rich_box <- cnm_mob_count_mat_sum %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Species Richness of Mobile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness")+
  theme_bw()
mobile_spec_rich_box
```


#ttest For Mobile Species Richness
```{r, ttest For Mobile Species Richness}
log_cnm_mob_count_mat <- cnm_mob_count_mat_sum %>% 
  mutate(spec_sum_add1 = spec_sum+1) %>% #adding a constant so I can eliminate the 0 i data
  mutate(log_spec_sum_add1 = log(spec_sum_add1)) #transforming data with log fxn
qqp(log_cnm_mob_count_mat$log_spec_sum_add1, "norm") #test for normality, the zero's aren't falling within normality test
shapiro.test(log_cnm_mob_count_mat$log_spec_sum_add1) #shapriro test shows low p value
mob_t_test <- t.test(log_spec_sum_add1~COL_pres, data = log_cnm_mob_count_mat)
mob_t_test
```


#Sessile Species Richnnes Data Manipulation 
```{r, Sessile Species Richnnes Data Manipulation}
cnm_sessile_count_mat 
cnm_sessile_count_mat$COL_pres <- as.factor(cnm_sessile_count_mat$COL_pres) #made this coulmn a factor
#cnm_sessile_count_mat$COL_pres_TF <- as.factor(cnm_sessile_count_mat$COL_pres_TF) #made this coulmn a factor THIS IMPORTANT FOR nMDS
cnm_sessile_count_mat$Transect<- as.factor(cnm_sessile_count_mat$Transect)

#cnm_sessile_count_mat_long <- cnm_sessile_count_mat %>% 
  #pivot_longer(cols = A_lugubris:L_gigantea, #pivoted to make longer
               #names_to = "Species", #all species name in this column
               #values_to = "Values") %>%  #all counts of said species in this column, this can give me a count per species to get species richness
  #filter(Values != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected againts since they had 0 for all species
 # group_by(COL_pres) %>% #group by presence or no presence of owl limpet
  #count(Species)

#Using this one
  cnm_sessile_count_mat_sum <- cnm_sessile_count_mat %>% 
  mutate(spec_sum = rowSums(across(c(A_elegantissima,Chthalmus_sp, Bare_rock, Ralfsia_sp, P_polymerus, Ulva_sp)), na.rm=TRUE))
```

#Boxplot of Sessile Species Richness
```{r, Boxplot of Sessile Species Richness}
sessile_spec_rich_box <- cnm_sessile_count_mat_sum %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Species Richness of Sessile Species in The Presence/Absence of Owl Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness")+
    geom_jitter(color = "purple", size=0.9, alpha=0.9, show.legend = (FALSE))+
  theme_bw()
sessile_spec_rich_box
```

#Species Richness of Sessile Welchs T test
```{r, Species Richness of Sessile Welchs T test}
log_cnm_sessile_count_mat <- cnm_sessile_count_mat_sum %>% 
  mutate(spec_sum_add1 = spec_sum+1) %>% #adding a constant so I can eliminate the 0 i data
  mutate(log_spec_sum_add1 = log(spec_sum_add1)) #transforming data with log fxn
qqp(log_cnm_sessile_count_mat$log_spec_sum_add1, "norm") #test for normality, the zero's aren't falling within normality test
shapiro.test(log_cnm_sessile_count_mat$log_spec_sum_add1) #shapriro test shows low p value
sessile_t_test <- t.test(log_spec_sum_add1~COL_pres, data = log_cnm_sessile_count_mat)
sessile_t_test
```

#Patchwork of species richness for mobiles and sessile
```{r, Patchwork of species richness for mobiles and sessile}
mobile_spec_rich_box_nolab <- cnm_mob_count_mat_sum %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = FALSE)+ 
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Mobiles",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness")+
  theme_bw()

sessile_spec_rich_nolab <- cnm_sessile_count_mat_sum %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Sessile",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness")+
    geom_jitter(color = "purple", size=0.9, alpha=0.9, show.legend = (FALSE))+
  theme_bw()


mobile_spec_rich_box_nolab+sessile_spec_rich_nolab+
  plot_annotation(title = 'Species Richness of Mobiles and Sessile Species in the Presence/Absence of Owl Limpets',
                  theme = theme(plot.title = element_text(size = 15)))
```

#Patchwork of Mobile Abundance and Sessile Percent Cover
```{r, Patchwork of Mobile Abundance and Sessile Percent Cover}
 patch_mob <- cnm_mobiles_sum_spec %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = Transect))+
  geom_boxplot(show.legend = FALSE)+ 
  scale_fill_brewer(palette = "Accent")+
  labs(title = "Abundance of Mobile Species",
       x = "Presence of Central Owl Limpet",
       y = "Abundance of Other Mobile Organisms") +
  theme_bw()

patch_sess <- cnm_sessile_sum_plot %>% 
  ggplot(aes(
    x = COL_pres,
    y = percent_cover,
    fill = Transect))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Accent")+
  labs(title = "Percent Cover of Sessile Species",
       x = "Presence of Central Owl Limpet",
       y = "Percent Cover") +
  theme_bw()

patch_mob+patch_sess+
  plot_annotation(title = 'Total Aundance of Mobiles Species and Percent Cover of Sessile Species in the Presence/Absence of Owl Limpets', theme = theme(plot.title = element_text(size = 15)))
```

