---
title: "2024_02_CNM_Winter"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

#Libraries
```{r, Libraries}
library("rerddap")
library(tidyverse)
library("tidync")
library("doParallel")
library(lubridate)
library(patchwork)
library(viridis)
library(here)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(emmeans)
library(agricolae)
library(vegan)
library(performance)
library(broom)
library(car)
library(lme4)
library(lmerTest)
library(pscl)
```

#Read in CSV
```{r, Read in CSV}
feb_cnm_shell_length <- read_csv(here("Data","2024_02_CNM_OL_SL_Data.csv"))
feb_cnm_mobiles_1 <- read_csv(here("Data","2024_02_CNM_Mobile_Data.csv"))
feb_cnm_sessile_1 <- read_csv(here("Data", "2024_02_CNM_Sessile_Data.csv"))
master_sl <- read_csv(here("Data","2023_09_CNM_OL_SL_Data.csv")) %>%
mutate(sex=ifelse(SL_mm>= 50, "female", "male"))
feb_cnm_mobiles <- read_csv(here("Data","2024_02_CNM_Mobile_Data.csv"))
feb_cnm_mob_count_mat <- read_csv(here("Data", "2024_02_CNM_Mobile_Count_Matrix.csv"))
feb_cnm_sessile_count_mat <- read_csv(here("Data", "2024_02_CNM_Sessile_Count_Matrix.csv"))
```

#Simple Statistics
```{r, Simple Statistics}
winter_data <- filter(master_sl, Season=="Winter")
feb_mean <- mean(winter_data$SL_mm)
fall_data <- filter(master_sl, Season=="Fall")
september_mean <- mean(fall_data$SL_mm)
max(feb_cnm_shell_length$SL_mm)
min(feb_cnm_shell_length$SL_mm)

master_sl
```

#Density
```{r, Density}
cnm_area_1 <- 140 # area (m^2) that I surveyed at Cabrillo National Monument Zone 3
feb_cnm_total_limpets <- nrow(feb_cnm_shell_length)
feb_pop_density_cnm <- feb_cnm_total_limpets/cnm_area_1 #calculate population density # of limpet/m^2
```

#Population Shell Length Distribution Graph
```{r, Population Shell Length Distribution Graph}
feb_cnm_pop_density <- feb_cnm_shell_length %>% #calling csv with shell length data
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="blue",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Owl Limpet Population, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(feb_cnm_mobiles_1$SL_mm),
             colour="green")#draw line where average lies on density
 feb_cnm_pop_density
```

#Size Distribution of Tagged Limpets
```{r, Size Distribution of Tagged Limpets}
feb_tagged_limpets <- feb_cnm_shell_length %>% #named new data frame using shell length data
  filter(Tag_ID != 0) #filtered out non-tagged limpets
feb_tagged_limpets #calling data frame
mean(feb_tagged_limpets$SL_mm)
```

#Tagged Limpets Shell Length Distribution Graph
```{r, #Tagged Limpets Shell Length Distribution Graph}
feb_tagged_distribution <- feb_tagged_limpets %>% #calling data frame with tagged limpets only
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="red",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Tagged Owl Limpets, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 9),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_y_continuous(breaks = c(0,2,4,6,8,10))+ #lines I want to show up on y axis
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(feb_tagged_limpets$SL_mm),
             colour="green")#draw line where average lies on density
feb_tagged_distribution
```

#Total number of tagged limpets
```{r, Total number of tagged limpets}
feb_tagged_limpets %>%
  group_by(Plot_Name) %>% 
  count(Tag_ID)
```

#February Size Density Graph
```{r, February Size Density Graph}
p <- feb_cnm_shell_length %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#FF6666", alpha = 0.6)+
  labs(title = "February")+
    theme_ipsum()

p
```
#February Density Graph
```{r, February Density Graph}
r <- feb_cnm_shell_length %>%
  ggplot( aes(x=SL_mm)) +
    geom_histogram(binwidth = 3, fill = "#70070e", color= "black")+
  labs(title = "February")+
    theme_ipsum()
r
```


#Septemeber Size Density Graph
```{r, Septemeber size Density Graph}
q <- fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#52B4C9", alpha = 0.6)+
  labs(title = "September")+
    theme_ipsum()

q
```

#Density of September
```{r, Density of September Graph}
s <- fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_histogram(binwidth = 3, fill = "#bf630d", color= "black")+
  labs(title = "September")+
    theme_ipsum()
s
```


#Patchwork of September and February Shell Length
```{r, Patchwork of September and February Shell Length}
q+p+
  plot_annotation(title = 'Shell Lenght Density of Owl Limpets in September and February', theme = theme(plot.title = element_text(size = 12)))
```
#Patwork of Fall and Winter Density
```{r, Patwork of Fall and Winter Density}
s+r
```


#Densiy of males and females
```{r, Density of males and females}
males_fall_data <- filter(master_sl, SL_mm < "50")
m_fall <- males_fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#05032b", alpha = 0.6)+
  labs(title = "Males")+
    theme_ipsum()
m_fall
```

#Density of females in Fall
```{r, Density of females in Fall}
females_fall_data <- filter(master_sl, SL_mm > "50")
f_fall <- females_fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#d10f46", alpha = 0.6)+
  labs(title = "Females")+
    theme_ipsum()
f_fall
```

#Patcwork of Fall Males and Females Density
```{r, Patcwork of Fall Males and Females Density}
m_fall+f_fall
```

#Density Plot of Males in Winter
```{r, Density Plot of Males in Winter}
males_winter_data <- filter(feb_cnm_shell_length, SL_mm < "50")
m_winter <- males_winter_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#3725db", alpha = 0.6)+
  labs(title = "Males")+
    theme_ipsum()
m_winter
```
#Density plot of females in winter
```{r, Density plot of females in winter}
females_winter_data <- filter(feb_cnm_shell_length, SL_mm > "50")
f_winter <- females_winter_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#f288c6", alpha = 0.6)+
  labs(title = "Females")+
    theme_ipsum()
f_winter
```

#Patchwork of males and females in winter
```{r, Patchwork of males and females in winter}
m_winter+f_winter
```

#Population Average Growth rate of Tagged Limpets from September to December
```{r, Growth rate of Tagged Limpets from September to December}
by_sex_data <- master_sl %>%
  group_by(Season, sex) %>%
  summarize(limpet_mean = mean(SL_mm, na.rm=TRUE)) %>% 
  pivot_wider(names_from = Season,
              values_from = limpet_mean) %>% 
  mutate(female_growth = (Winter-Fall)/4.75)



growth_sl <- master_sl %>% 
  filter(Date != "2024_02",
         Tag_ID !=0) %>% 
  unite(season_tag, c(Season, Tag_ID))
growth_sl

initial_new <- (feb_mean - september_mean)
day_growth_rate <- initial_new/72 #rate per day
day_growth_rate
week_growth_rate<- initial_new/19
week_growth_rate
month_grow_rate <- initial_new/4.75
month_grow_rate
```

#Boxplot of Raw Density
```{r}
sep_feb_master <- filter(master_sl, Date != "2023_12")

raw_density <- sep_feb_master %>%
  ggplot(aes(x = as.factor(Season), y = SL_mm, fill = Season))+
  geom_boxplot()+
  labs(title = "Raw Density",
       fill = "Season",
       x = "Season")+
  theme(plot.title = element_text(size = 8),
        axis.title.x = element_text(size = 7),
        axis.text.x = element_text(size = 6))
raw_density
```

```{r}
m <- master_sl %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(aes(fill = Season), alpha = 0.6)+
  #labs()+
    theme_ipsum()

m
```

```{r}
summary_data_1 <- master_sl %>% 
  group_by(Plot_Name, Season) %>%
  mutate(Mean_Plot = mean(SL_mm),
         SD_Plot = sd(SL_mm),
         SE_Plot = SD_Plot/sqrt(ncol(master_sl)))
summary_data_1


summary_data <- master_sl %>%
  group_by(Season, Plot_Name, sex) %>%
  count() %>%
  group_by(Season, sex) %>%
  summarize(limpet_mean = mean(n, na.rm=TRUE),
            limpet_se = sd(n, na.rm=TRUE)/sqrt(n()))

summary_data

s <- summary_data %>%
  ggplot(aes(x=Season,
             y=limpet_mean,
             color=sex))+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=limpet_mean-limpet_se,
                    ymax=limpet_mean+limpet_se),
                width=0.1)
s

```

#LMER of mobile species
```{r}
feb_cnm_mobiles_long <- feb_cnm_mobiles %>% 
  pivot_longer(cols = M_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count") %>%  #all counts of said species in this column, this can give me a count per species to get species richness
  filter(Count != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected against since they had 0 for all species
  group_by(Transect, COL_pres) %>% 
  count(Species)# %>% #provide count of each species by group
  #mutate(Spec_rich = (n/1963.5)*100)

##########THIS IS THE ONE THAT WORKS############
feb_cnm_mobiles_sum_spec <- feb_cnm_mobiles %>% 
  mutate(spec_sum = rowSums(across(c(M_lugubris, L_dentiens, L_plena, L_keenae, L_limatula, L_scabra, Nuttallina_sp, Mopalia_sp, P_crassipes, T_eiseni, T_funebralis, T_gallina, L_gigantea)), na.rm=TRUE)) %>% 
   pivot_longer(cols = M_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Count")

lmer_mob_abun <- lmer(spec_sum~COL_pres+(1|Transect), data = feb_cnm_mobiles_sum_spec)
anova(lmer_mob_abun)
summary(lmer_mob_abun)
```

#Boxplot of Mobile Organism Abundance Per Plot in Presence/Absence of Central Limpet
```{r,Boxplot of Mobile Organism Abundance Per Plot in Presence/Absence of Central Limpet}
 feb_cnm_mobiles_sum_spec %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = COL_pres))+
  geom_boxplot(show.legend = FALSE)+ 
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Abundance of Other Mobile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Abundance of Other Mobile Organisms") +
  theme_bw()
  
```

#Sessile Species Abundance Using Percent Cover
```{r, Sessile Species Abundance}
#Make columns into factors
feb_cnm_sessile_1$COL_pres <- as.factor(feb_cnm_sessile_1$COL_pres) #made this column a factor THIS IMPORTANT FOR nMDS
feb_cnm_sessile_1$Transect<- as.factor(feb_cnm_sessile_1$Transect)


feb_cnm_sessile_sum_plot <- feb_cnm_sessile_1 %>%
  mutate(spec_sum = rowSums(across(c(Anthopleura_elegantissima,Phragmatopoma_californica, Balanus_glandula, Chthalmus, Bare_rock, Brown_encrusting, Coralline_crust, Endocladia_sp, Goose_neck, Ulva)), na.rm=TRUE))%>% 
  mutate(percent_animal = (Anthopleura_elegantissima+ Phragmatopoma_californica+ Balanus_glandula+ Goose_neck+ Chthalmus)/spec_sum*100,
         percent_algae = (Brown_encrusting+Coralline_crust+Endocladia_sp+Ulva)/spec_sum*100)

lmer_sess_an_abun <- lmer(percent_animal~COL_pres+(1|Transect), data = feb_cnm_sessile_sum_plot)
anova(lmer_sess_an_abun)
summary(lmer_sess_an_abun)

lmer_sess_alg_abun <- lmer(percent_algae~COL_pres+(1|Transect), data = feb_cnm_sessile_sum_plot)
anova(lmer_sess_alg_abun)
summary(lmer_sess_alg_abun)

```

#Boxplot of Sessile Organism Percent Cover Per Plot in Presence/Absence of Central Limpet
```{r, Boxplot of Sessile Organism Percent Cover Per Plot in Presence/Absence of Central Limpet}
feb_cnm_sessile_sum_plot %>% 
  pivot_longer(cols = c(percent_animal, percent_algae), names_to = "percent_type")%>%
  ggplot(aes(
    x = COL_pres,
    y = value,
    fill = COL_pres,
    color = percent_type))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Pastel")+
  scale_color_brewer(palette = "Set1")+
  labs(title = "Percent Cover of Sessile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Percent Cover") +
  theme_bw()

```

#Permanova of Mobile Species Matrix
```{r, Permanova of Mobile Species Matrix}
feb_cnm_mob_count_mat$COL_pres <- as.factor(feb_cnm_mob_count_mat$COL_pres) #made this coulmn a factor
feb_cnm_mob_count_mat$Transect<- as.factor(feb_cnm_mob_count_mat$Transect)

feb_cnm_mob_count_sum <- feb_cnm_mob_count_mat%>% #I created a new data frame with the addition of the sum of counts per species in each plot using a data matrix made up of 0 and 1. 1 represents the occurence of that species in that plot.
  mutate(Sum = sum(M_lugubris, L_dentiens, L_plena, L_keenae, L_limatula, L_scabra, Nuttallina_sp, Mopalia_sp, P_crassipes, T_eiseni, T_funebralis, T_gallina, L_gigantea)) %>% 
  filter(Sum != 0) #permanova did not accept 0

model2<-adonis2(feb_cnm_mob_count_sum[,-c(1:13)]~COL_pres, feb_cnm_mob_count_sum, permutations = 999, method="bray") #independent variable is the presence or absence of limpets
model2
```

#Species Richness of Mobiles
```{r, Species Richness of Mobiles}
feb_cnm_mob_count_mat$COL_pres <- as.factor(feb_cnm_mob_count_mat$COL_pres) #made this coulmn a factor
feb_cnm_mob_count_mat$Transect<- as.factor(feb_cnm_mob_count_mat$Transect)

feb_cnm_mob_count_mat_long <- feb_cnm_mob_count_mat %>% 
  pivot_longer(cols = M_lugubris:L_gigantea, #pivoted to make longer
               names_to = "Species", #all species name in this column
               values_to = "Values") %>%  #all counts of said species in this column, this can give me a count per species to get species richness
  filter(Values != 0) %>% #take out any rows that have a count of 0, R was giving me problems. Some plots were selected againts since they had 0 for all species
  group_by(COL_pres) %>% #group by presence or no presence of owl limpet
  count(Species)

#USE THIS ONE
feb_cnm_mob_count_mat_sum <- feb_cnm_mob_count_mat %>% 
  mutate(spec_sum = rowSums(across(c(M_lugubris, L_dentiens, L_plena, L_keenae, L_limatula, L_scabra, Nuttallina_sp, Mopalia_sp, P_crassipes, T_eiseni, T_funebralis, T_gallina, L_gigantea)), na.rm=TRUE))
```

#Species Richness of Mobiles Boxplot
```{r, Species Richness of Mobiles Boxplot}
feb_mobile_spec_rich_box <- feb_cnm_mob_count_mat_sum %>% 
  ggplot(aes(
    x = COL_pres,
    y = spec_sum,
    fill = COL_pres))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Dark2")+
  labs(title = "Species Richness of Mobile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness")+
  theme_bw()
feb_mobile_spec_rich_box
```

#LMER For Mobile Species Richness
```{r}
#lmer
feb_mob_spec_rich <- lmer(spec_sum~COL_pres+(1|Transect), data = feb_cnm_mob_count_mat_sum)
anova(feb_mob_spec_rich)
summary(feb_mob_spec_rich)
```
#Sessile Species Richnnes Data Manipulation 
```{r, Sessile Species Richnnes Data Manipulation}
feb_cnm_sessile_count_mat$COL_pres <- as.factor(feb_cnm_sessile_count_mat$COL_pres) #made this coulmn a factor
feb_cnm_sessile_count_mat$Transect<- as.factor(feb_cnm_sessile_count_mat$Transect)

#Using this one
feb_cnm_sessile_count_mat_sum <- feb_cnm_sessile_count_mat %>% 
    select(Transect, Plot_Name, L_R, Meter_no, COL_pres, Tag_ID, Anthopleura_elegantissima,Phragmatopoma_californica, Balanus_glandula, Chthalmus, Brown_encrusting, Coralline_crust, Endocladia_sp, Goose_neck, Ulva ) %>% 
  mutate(spec_sum = rowSums(across(c(Anthopleura_elegantissima,Phragmatopoma_californica, Balanus_glandula, Chthalmus, Brown_encrusting, Coralline_crust, Endocladia_sp, Goose_neck, Ulva)), na.rm=TRUE))

####Try this###
feb_cnm_sessile_matrix <- feb_cnm_sessile_count_mat %>%
  mutate(spec_sum = rowSums(across(c(Anthopleura_elegantissima,Phragmatopoma_californica, Balanus_glandula, Chthalmus, Bare_rock, Brown_encrusting, Coralline_crust, Endocladia_sp, Goose_neck, Ulva)), na.rm=TRUE))%>% 
  mutate(animal = (Anthopleura_elegantissima+ Phragmatopoma_californica+ Balanus_glandula+ Goose_neck+ Chthalmus),
         algae = (Brown_encrusting+Coralline_crust+Endocladia_sp+Ulva))

```

#Boxplot of Sessile Species Richness
```{r, Boxplot of Sessile Species Richness}
feb_cnm_sessile_matrix %>% 
  pivot_longer(cols = c(animal, algae), names_to = "sessile_type")%>%
  ggplot(aes(
    x = COL_pres,
    y = value,
    fill = COL_pres,
    color = sessile_type))+
  geom_boxplot(show.legend = TRUE)+ 
  scale_fill_brewer(palette = "Pastel1")+
  scale_color_brewer(palette = "Set1")+
  labs(title = "Percent Cover of Sessile Species in Presence/Absence of Central Limpet",
       x = "Presence of Central Owl Limpet",
       y = "Species Richness") +
  theme_bw()

```

#Species Richness of Sessile Welchs T test
```{r, Species Richness of Sessile Welchs T test}
log_feb_cnm_sessile_count_mat <- feb_cnm_sessile_count_mat_sum %>% 
  mutate(spec_sum_add1 = spec_sum+1) %>% #adding a constant so I can eliminate the 0 i data
  mutate(log_spec_sum_add1 = log(spec_sum_add1)) #transforming data with log fxn
qqp(log_feb_cnm_sessile_count_mat$log_spec_sum_add1, "norm") #test for normality, the zero's aren't falling within normality test
shapiro.test(log_feb_cnm_sessile_count_mat$log_spec_sum_add1) #shapriro test shows low p value
sessile_t_test <- t.test(log_spec_sum_add1~COL_pres, data = log_feb_cnm_sessile_count_mat)
sessile_t_test

model5_sess_rich <- lmer(percent_animal~COL_pres+(1|Transect), data = feb_cnm_sessile_sum_plot)
anova(model5_sess_rich)
summary(model5_sess_rich)
```