---
title: "2024_02_CNM_Winter"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

#Libraries
```{r, Libraries}
library("rerddap")
library(tidyverse)
library("tidync")
library("doParallel")
library(lubridate)
library(patchwork)
library(viridis)
library(here)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(emmeans)
library(agricolae)
library(vegan)
library(performance)
library(broom)
library(car)
library(lme4)
library(lmerTest)
```

#Read in CSV
```{r, Read in CSV}
feb_cnm_shell_length <- read_csv(here("Data","2024_02_CNM_OL_SL_Data.csv"))
feb_cnm_mobiles_1 <- read_csv(here("Data","2024_02_CNM_Mobile_Data.csv"))
feb_cnm_sessile_1 <- read_csv(here("Data", "2024_02_CNM_Sessile_Data.csv"))
master_sl <- read_csv(here("Data","2023_09_CNM_OL_SL_Data.csv"))
```

#Simple Statistics
```{r, Simple Statistics}
feb_mean <- mean(feb_cnm_shell_length$SL_mm)
fall_data <- filter(master_sl, Season=="Fall")
september_mean <- mean(fall_data$SL_mm)
max(feb_cnm_shell_length$SL_mm)
min(feb_cnm_shell_length$SL_mm)
```

#Density
```{r, Density}
cnm_area_1 <- 140 # area (m^2) that I surveyed at Cabrillo National Monument Zone 3
feb_cnm_total_limpets <- nrow(feb_cnm_shell_length)
feb_pop_density_cnm <- feb_cnm_total_limpets/cnm_area_1 #calculate population density # of limpet/m^2
```

#Population Shell Length Distribution Graph
```{r, Population Shell Length Distribution Graph}
feb_cnm_pop_density <- feb_cnm_shell_length %>% #calling csv with shell length data
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="blue",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Owl Limpet Population, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(feb_cnm_mobiles_1$SL_mm),
             colour="green")#draw line where average lies on density
 feb_cnm_pop_density
```

#Size Distribution of Tagged Limpets
```{r, Size Distribution of Tagged Limpets}
feb_tagged_limpets <- feb_cnm_shell_length %>% #named new data frame using shell length data
  filter(Tag_ID != 0) #filtered out non-tagged limpets
feb_tagged_limpets #calling data frame
mean(feb_tagged_limpets$SL_mm)
```

#Tagged Limpets Shell Length Distribution Graph
```{r, #Tagged Limpets Shell Length Distribution Graph}
feb_tagged_distribution <- feb_tagged_limpets %>% #calling data frame with tagged limpets only
  select(Limpet_No, SL_mm) %>% #selecting limpet number to count and shell length
  ggplot( aes(x=SL_mm)) + #Sl on x, I am not selecting y so R can use limpet count for density plot
  geom_bar(fill="red",#color of bars
           colour="black",#color of bar outline
           alpha= 1,#transparency of bar
           width = 1) + #size of bars
  labs(title = "Size Distribution of Tagged Owl Limpets, Cabrillo National Monument",
       x = "Shell Length (mm)",
       y = "Owl Limpet Count")+
  theme(plot.title = element_text(size = 9),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7))+
  scale_y_continuous(breaks = c(0,2,4,6,8,10))+ #lines I want to show up on y axis
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80))+ #lines I want to show up on x axis
  geom_vline(xintercept = mean(feb_tagged_limpets$SL_mm),
             colour="green")#draw line where average lies on density
feb_tagged_distribution
```

#Total number of tagged limpets
```{r, Total number of tagged limpets}
feb_tagged_limpets %>%
  group_by(Plot_Name) %>% 
  count(Tag_ID)
```

#February Size Density Graph
```{r, February Size Density Graph}
p <- feb_cnm_shell_length %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#FF6666", alpha = 0.6)+
  labs(title = "February")+
    theme_ipsum()

p
```
#February Density Graph
```{r, February Density Graph}
r <- feb_cnm_shell_length %>%
  ggplot( aes(x=SL_mm)) +
    geom_histogram(binwidth = 3, fill = "#70070e", color= "black")+
  labs(title = "February")+
    theme_ipsum()
r
```


#Septemeber Size Density Graph
```{r, Septemeber size Density Graph}
q <- fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#52B4C9", alpha = 0.6)+
  labs(title = "September")+
    theme_ipsum()

q
```

#Density of September
```{r, Density of September Graph}
s <- fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_histogram(binwidth = 3, fill = "#bf630d", color= "black")+
  labs(title = "September")+
    theme_ipsum()
s
```


#Patchwork of September and February Shell Length
```{r, Patchwork of September and February Shell Length}
q+p+
  plot_annotation(title = 'Shell Lenght Density of Owl Limpets in September and February', theme = theme(plot.title = element_text(size = 12)))
```
#Patwork of Fall and Winter Density
```{r, Patwork of Fall and Winter Density}
s+r
```


#Densiy of males and females
```{r, Density of males and females}
males_fall_data <- filter(master_sl, SL_mm < "50")
m_fall <- males_fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#05032b", alpha = 0.6)+
  labs(title = "Males")+
    theme_ipsum()
m_fall
```

#Density of females in Fall
```{r, Density of females in Fall}
females_fall_data <- filter(master_sl, SL_mm > "50")
f_fall <- females_fall_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#d10f46", alpha = 0.6)+
  labs(title = "Females")+
    theme_ipsum()
f_fall
```

#Patcwork of Fall Males and Females Density
```{r, Patcwork of Fall Males and Females Density}
m_fall+f_fall
```

#Density Plot of Males in Winter
```{r, Density Plot of Males in Winter}
males_winter_data <- filter(feb_cnm_shell_length, SL_mm < "50")
m_winter <- males_winter_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#3725db", alpha = 0.6)+
  labs(title = "Males")+
    theme_ipsum()
m_winter
```
#Density plot of females in winter
```{r, Density plot of females in winter}
females_winter_data <- filter(feb_cnm_shell_length, SL_mm > "50")
f_winter <- females_winter_data %>%
  ggplot( aes(x=SL_mm)) +
    geom_density(fill = "#f288c6", alpha = 0.6)+
  labs(title = "Females")+
    theme_ipsum()
f_winter
```

#Patchwork of males and females in winter
```{r, Patchwork of males and females in winter}
m_winter+f_winter
```

#Population Average Growth rate of Tagged Limpets from September to December
```{r, Growth rate of Tagged Limpets from September to December}
growth_sl <- master_sl %>% 
  filter(Date != "2024_02",
         Tag_ID !=0) %>% 
  unite(season_tag, c(Season, Tag_ID))

initial_new <- (feb_mean - september_mean)
day_growth_rate <- initial_new/72 #rate per day
day_growth_rate
month_growth_rate<- initial_new/10
month_growth_rate
```

#Boxplot of Raw Density
```{r}
sep_feb_master <- filter(master_sl, Date != "2023_12")

raw_density <- sep_feb_master %>%
  ggplot(aes(x = as.factor(Season), y = SL_mm, fill = Season))+
  geom_boxplot()+
  labs(title = "Raw Density",
       fill = "Season",
       x = "Season")+
  theme(plot.title = element_text(size = 8),
        axis.title.x = element_text(size = 7),
        axis.text.x = element_text(size = 6))
raw_density
```

